Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-12 arxiv/experiments.tex
section 1.1 wip
finish section 1.1

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
	\caption{Validating Example \ref{ex_same_cov} in the same covariates case: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$. \FY{What is $t$ in this setting?}}
	\label{fig_same_cov}
\end{figure}

@@

\paragraph{Sample ratio.}
Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are reasonably accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The  task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is \FY{What is $\kappa^2$?}. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.  Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}.

@@

\begin{figure}[!t]
%		\begin{subfigure}[b]{0.32\textwidth}
%		\centering
%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
%		\caption{Sample efficiency}
%		\label{fig_model_shift}
%	\end{subfigure}\hfill
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_c2_400.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in the different covariates case:
	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
	In Figure \ref{fig_size}, we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
	We observe that task two's prediction loss decreases initially before increasing again. Our result shows (provably) that this phenomenon occurs due to different bias-variance tradeoffs as the sample ratio increases.
	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one. Otherwise, having covariate shift decreases task two's prediction loss (surprisingly).}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

\paragraph{Sample ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.

>>>>

\begin{figure}[!t]
	\centering
	\includegraphics[width=0.45\textwidth]{figures/same_covariates.eps}
	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
	\label{fig_same_cov}
\end{figure}

@@

\paragraph{Sample ratio.}
Second, we show how varying sample ratio impacts hard parameter sharing in the setting of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
Again, our estimates are reasonably accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance is $d^2 = 0.08$, the noise variance is $\sigma^2 = 0.3^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increases when the sample ratio is above certain level.
On the other hand, when $d^2 = 0.045$, task two's prediction loss decreases monotonically.
Our work explains this trend as discussed below Corollary \ref{cor_MTL_loss}. \HZ{check}

@@

\begin{figure}[!t]
%		\begin{subfigure}[b]{0.32\textwidth}
%		\centering
%		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
%		\caption{Sample efficiency}
%		\label{fig_model_shift}
%	\end{subfigure}\hfill
	\centering
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/sample_ratio_several_d.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Validating Example \ref{ex_sample_ratio} and Example \ref{ex_covshift} in Section \ref{sec_diff} for two tasks:
	in both experiments, our estimated losses (solid line) match the empirical losses (dotted line) accurately.
	In Figure \ref{fig_size}, we discover several interesting phenomena by fixing task two's sample size and increasing task one's sample size.
	Depending on how large $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
	In Figure \ref{fig_covariate}, we show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shift increases task two's prediction loss when task two's sample size is larger than task one. Otherwise, having covariate shift (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure}

@@

\paragraph{Sample size ratio.}
In Figure \ref{fig_ab_data}, we observe that for multiple example task pairs, increasing task one's sample size improves task two's prediction accuracy initially, but hurts eventually.
On the $y$-axis, we plot task two's test accuracy using HPS, subtracted by its STL test accuracy.
%validate that as we increase the sample ratio while keeping task two's sample size fixed, task two's prediction accuracy does not always increase.
We fix task one's sample size at $1000$ and increase task two's sample size from $100$ to $3000$.
These examples and the one in Figure \ref{fig_size} suggest a natural progressive training schedule, where we add samples progressively until performance drops:
%In particular, Figure \ref{fig_size} (and our analysis) shows that $L(\hat{\beta}_t^{\MTL})$ behaves as a quadratic function over $\rho_1$.
%More generally, depending on how large $\Psi(\beta_1, \beta_2)$ is, $L(\hat{\beta}_t^{\MTL})$ may also be monotonically increasing or decreasing.
%Based on this observation, we propose a progressive training schedule to improve the compuational efficiency of hard parameter sharing.
\begin{itemize}
	\item We divide the source task data into $S$ batches.
	For $S$ rounds, we incrementally add the source task data by adding one batch at a time.
	\item After training $T$ epochs, if the validation accuracy becomes worse than the previous round's result, we terminate.
%	Algorithm \ref{alg_inc_train} in Appendix \ref{app_experiments} describes the procedure in detail.
\end{itemize}
For example, if we apply this procedure to the settings of Figure \ref{fig_ab_data} and \ref{fig_size}, it will terminate until reaching the optimal sample ratio.
The advantage of this procedure is that it reduces the computational cost compared to standard round-robin training schedules.
